Are kelp forests different? A comparison of kelp forests between contrasting study sites

### 2018-07-13 paper_draft.Rmd
edit

library(tidyverse)
library(vegan)
library(ggplot2)
library(reshape2)
library(gridExtra)

@@

flora_df <- read.csv(file = "data/flora.csv", check.names = FALSE)
fauna_df <- read.csv(file = "data/fauna.csv", check.names = FALSE)
benthic <- read.csv(file = "data/benthic.csv", check.names = FALSE)
cover_df <- read.csv(file = "data/cover.csv", check.names = FALSE)
kelp_df <- read.csv(file = "data/kelp.csv", check.names = FALSE)
urchin_df <- fauna_df[ , 28]

flora_lng <- melt(data = flora_df, value.name = "biomass", id.vars = c("site", "id"), variable.name = "species")

@@

```{r diversity graphs script, message=FALSE, warning=FALSE, paged.print=FALSE}

plot_flora <- ggplot(data = flora_lng, aes(x=id, y=species, colour = site, size =biomass)) +                   geom_point() + 
              theme(axis.text.x=element_text(angle = 90, hjust = 1, vjust = 0.3)) +
              theme(panel.background = element_rect(fill = 'grey', colour = 'grey')) +
              ylab("Species") + 
              xlab("ID")

fauna_lng <- melt(data = fauna_df, value.name = "biomass", id.vars = c("site", "id"), variable.name = "species")

plot_fauna <- ggplot(data = fauna_lng, aes(x=site, y=biomass, colour = species)) +                             stat_summary(geom = "pointrange", data = fauna_lng) + 
              theme(axis.text.x=element_text(angle = 90, hjust = 1, vjust = 0.3)) +
              theme(panel.background = element_rect(fill = 'grey', colour = 'grey')) +
              ylab("") + 
              xlab("") +
              coord_flip()
grid.arrange(plot_flora, plot_fauna)

```
+ stat_summary(fun.y="sum", geom="point")
levels(droplevels(subdf$letters))

>>>>

library(tidyverse)
library(vegan)
library(ggplot2)
library(reshape2)
library(ggpubr)

@@

flora_df <- read.csv(file = "data/flora.csv", check.names = FALSE)
fauna_df <- read.csv(file = "data/fauna.csv", check.names = FALSE)
fauna_df <- fauna_df[ ,c(1:27)]
benthic <- read.csv(file = "data/benthic.csv", check.names = FALSE)
cover_df <- read.csv(file = "data/cover.csv", check.names = FALSE)
kelp_df <- read.csv(file = "data/kelp.csv", check.names = FALSE)

flora_lng <- melt(data = flora_df, value.name = "biomass", id.vars = c("site", "id"), variable.name = "species") 
fauna_lng <- melt(data = fauna_df, value.name = "biomass", id.vars = c("site", "id"), variable.name = "species")

@@

Diveristy of flora was...

```{r diversity fauna script, message=FALSE, warning=FALSE, paged.print=FALSE}

plot_flora <- ggplot(data = flora_lng, aes(x = species, y= biomass, fill = site)) + 
              geom_bar(stat = "identity", show.legend = FALSE, position=position_dodge()) + 
              theme(axis.text.x=element_text(angle = 90, hjust = 1, vjust = 0.3)) +
              theme(panel.background = element_rect(fill = 'grey', colour = 'black')) +
              ylab("Flora") + 
              xlab("") +
              coord_flip()
```

Diveristy of fauna was...

```{r}

plot_fauna <- ggplot(data = fauna_lng, aes(x = species, y= biomass, fill = site)) + 
              geom_bar(stat = "identity", show.legend = FALSE ,position=position_dodge(),
              size=.3) + 
              theme(axis.text.x=element_text(angle = 90, hjust = 1, vjust = 0.3)) +
              theme(panel.background = element_rect(fill = 'grey', colour = 'black')) +
              ylab("Fauna") + 
              xlab("") +
              coord_flip()
```

```{r biomass barplot, message=FALSE, warning=FALSE, paged.print=FALSE}
ggarrange(plot_flora, plot_fauna)
```
